### 2020-02-25 README.Rmd
Change to make get_model_specs more flexible

```{r}
# Read in Big Woods census data from 2008 & 2014
bw_2008 <- 
  "https://deepblue.lib.umich.edu/data/downloads/z603qx485" %>% 
  read_delim(delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )
bw_2014 <- 
  "https://deepblue.lib.umich.edu/data/downloads/1831ck00f" %>% 
  read_delim(delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )

# Read in bigwoods grouping classification data
bw_species <- 
  "https://deepblue.lib.umich.edu/data/downloads/000000086" %>% 
  read_delim(delim = "\t") %>% 
  # convert all to snake case:
  mutate_at(c("species", "genus", "family", "idlevel", "spcode"), to_any_case) %>% 
  # join trait group
  left_join(families, by = c("spcode", "family")) %>% 
  mutate(
    sp = str_sub(genus, 1, 2), 
    sp = str_c(sp, str_sub(species, 1, 2)),
    sp = tolower(sp),
    latin = str_c(genus, species, sep = " "),
    latin = to_any_case(latin)
  ) %>% 
  select(sp, spcode, genus, species, latin, family, trait_group)
```

@@

* Model formula: Growth as a function of

>>>>

```{r}
# Read in Big Woods census data from 2008 & 2014
bw_2008 <- 
  "https://deepblue.lib.umich.edu/data/downloads/z603qx485" %>% 
  read_delim(delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>%
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )
bw_2014 <- 
  "https://deepblue.lib.umich.edu/data/downloads/1831ck00f" %>% 
  read_delim(delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>%
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )

# Read in bigwoods grouping classification data
bw_species <- 
  "https://deepblue.lib.umich.edu/data/downloads/000000086" %>% 
  read_delim(delim = "\t") %>% 
  # convert all to snake case:
  mutate_at(c("species", "genus", "family", "idlevel", "spcode"), to_any_case) %>% 
  # join trait group
  left_join(families, by = c("spcode", "family")) %>% 
  mutate(
    sp = str_sub(genus, 1, 2), 
    sp = str_c(sp, str_sub(species, 1, 2)),
    sp = tolower(sp),
    latin = str_c(genus, species, sep = " "),
    latin = to_any_case(latin)
  ) %>% 
  select(sp = spcode, genus, species, latin, family, trait_group)

bw_2008 <- bw_2008 %>%
  left_join(bw_species,by='sp')

```

@@

Next we specify the growth model we want. We will model growth as a function of tree identiy, size, and the size and identiy of its neighbors. The model can be run on different grouping of individuals (e.g., based on species or trait groupings). It can also be run with different measures of competition.

* `model_number = 1`: No competition growth only depends on `dbh` and individual grouping.
* `model_number = 2`: Competition but identity of competitor does not matter, just sum of competitior biomass.
* `model_number = 3`: Full model with competition and competitor identity.

```{r}
bw_specs <- get_model_specs(bw_2008, 3, 'trait_group')
bw_specs

scbi_specs <- get_model_specs(scbi_2013, 3, 'sp')

```
